\documentclass[12pt, oneside]{article} 
\usepackage{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,      
    urlcolor=blue,
}
 
\urlstyle{same}

\geometry{letterpaper, margin=0.5in} 
\title{A survey of scikit-learn tree-related pull requests}
\author{Nelson Liu \\
  University of Washington \\
  nfliu@uw.edu }
\begin{document}
\maketitle
\section{Introduction}
While reviewing the various tree-related pull requests to evaluate
which would make good candidates for a Google Summer of Code project,
I figured it would be prudent to keep a written log of my thoughts
regarding the various pull requests.\\
To find pull requests to work on, I ran a GitHub search with the
keywords \texttt{'tree' is:pr is:open}. My search filters were
extremely loose and they literally captured any reference of
tree. This resulted in a lot of code regarding nearest neighbors / the
source tree in general to pop up, but I figured that its better to
cast a wider net to ensure that I don't miss any potential work to be
done. The pull requests fetched are listed below in order from oldest
to newest. I used this method of ordering because I figured that older
pull requests are also more likely to be stale, which would make them
good candidates for a GSoC project.

\section{Tree-related pull requests and associated commentary}
\begin{enumerate}
  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/911}
    {\#911 WIP: Covariance Updates}}\\
  Commentary: This pull request doesn't seem too relevant, although
  its development seems to have stalled. Last substantive comment was
  in July 2013.
  
  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/941}
    {\#941 Adding a pruning method to the tree}}\\
  Commentary: This pull request seems well suited to a Google Summer of Code
  project. Throughout the thread, the developers were in support of
  its implementation. It's also seem to have gone quite stale, the
  tree class has changed considerably since this PR was first written
  and the author seems to have given up development. \textbf{All in
    all, this seems like a great pull request to pick up for Google
    Summer of Code}

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/1386}
    {\#1368 WIP: Implement ROC-SVM linear pairwise ranking loss with SGD}}\\
  Commentary: This pull request deals with SGD, and is not quite
  relevant to my proposed theme of ``tree'' as a result. Seems to have
  gone stale, with little interest in revitalizing it from the
  outside.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/1454}
    {\#1454 MRG+1: Add resample to preprocessing}}\\
  Commentary: This pull request doesn't deal with the tree module,
  although it seems mostly completed and is waiting for another review
  before merging (@agramfort already +1'd).

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/1574}
    {\#1574 WIP: sample\_weight support}}\\
  Commentary: This pull request doesn't deal with the tree module, and
  seems to have gone stale with a fair amount of work left to be
  done. Many of its ideas seem to have been proposed / implemented in
  more recent pull requests, however (see the myriad of references at
  the bottom of the pull request).

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/1742}
    {\#1742 MRG Training Score in Gridsearch}}\\
  Commentary: This pull request doesn't deal with the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/1830}
    {\#1830 MRG: Evidence Accumulation Clustering}}\\
  Commentary: This pull request doesn't deal with the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/1984}
    {\#1984 Implementation of OPTICS}}\\
  Commentary: This pull request doesn't deal with the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2043}
    {\#2043 OPTICS clustering}}\\
  Commentary: This pull request doesn't deal with the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2285}
    {\#2285 [WIP] Earth (MARS)}}\\
  Commentary: This pull request doesn't deal with the tree module.
  
  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2391}
    {\#2391 [MRG] Implemented Determinant ECOC}}\\
  Commentary: This pull request doesn't deal with the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2461}
    {\#2461 [MRG] Label power set multilabel classification strategy}}\\
  Commentary: This pull request doesn't deal with the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2530}
    {\#2530 [MRG] sklearn.tree.export\_dict for converting Tree
      objects into a jsonable format}}\\
  Commentary: This pull request is a proposal for a method for
  converting tree objects to JSON. The associated PR discussion
  eventually concluded that there have been no exports in the main
  project, and that it was unfit to be in the main
  repo. @GaelVaroquaux suggested that it was out of scope, but it
  might be useful to have PMML export of trees from scikit-learn. This
  has been since completed in a separate project with some relevant
  discussion at
  \href{https://github.com/scikit-learn/scikit-learn/issues/1596}{\#1596}.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2567}
    {\#2567 Issue \#2559: Added normalize option to LogisticRegression}}\\
  Commentary: This pull request doesn't deal with the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2580}
    {\#2580 [WIP] first cut at LambdaMART}}\\
  Commentary: This pull request doesn't deal with the tree
  module. Seems to have gone stale, although there appears to be some
  lingering interest in its implementation. @mblondel did however
  express that he has had some bad experiences with LambdaMART, and
  that it "performs either worse or comparably to random forests or
  gradient boosting".


  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2784}
    {\#2784 Liblinear Sample Weights}}\\
  Commentary: This pull request doesn't deal with the tree module,
  although work seems to have gone stale. It has since been picked up
  by @mechcoder, and he has made a few PRs toward its completion.


  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/2567}
    {\#2567 Issue \#2559: Added normalize option to LogisticRegression}}\\
  Commentary: This pull request doesn't deal with the tree module.

  
  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/3306}
    {\#3306 [MRG] Google Summer of Code 2014: Standard Extreme Learning Machines}}\\
  Commentary: This pull request doesn't deal with the tree module, and
  seems mostly implemented.


  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/3346}
    {\#3346 [WIP] Categorical split for decision tree}}\\
  Commentary: This pull request is extremely relevant to the tree
  module. The original author of this PR seems to have abandoned
  development, and it was subsequently reproposed in
  \href{https://github.com/scikit-learn/scikit-learn/pull/4899}{\#4899
    NOCATS: Categorical splits for tree-based learners}, which is
  still in active development.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/3436}
    {\#3436 ENH: Added Random Forest feature importance based on out
      of bag data}}\\
  Commentary: This pull request doesn't have any commentary from core
  devs or even other developers, so I can't tell if it would be well
  received as an enhancement. However, it was referenced in issue
  \href{https://github.com/scikit-learn/scikit-learn/issues/3455}{\#3455},
  which was subsequently picked up and seemingly abandoned in
  \href{https://github.com/scikit-learn/scikit-learn/pull/3723}{\#3723}. \textbf{I'm
  on the fence as to whether this would be a suitable Google Summer of Code project, as
  it isn't quite related to trees but seems somewhat useful
  nonetheless. It's difficult to tell without more comments on the
  matter from core devs, particularly @amueller and @larsmans as they
  designed the scorer API}

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/3464}
    {\#3464 Added Example for Plotting Hierarchical Clustering Dendrogram}}\\
  Commentary: This pull request doesn't quite deal with the tree
  module, but is nonetheless an interesting example that plots the
  hierarchical clustering dendrogram. This is useful because
  hierarchical cluster is one of the few clustering algorithms where
  adding structure results in speed improvements. \textbf{This might
    be out of the scope of my Google Summer of Code project on trees, but it's a very
    interesting project that has stalled due to missing (now present)
    functionality. Should be tagged as "Need Contributor", or I could
    possibly find some time on the side to work on it.}


  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/3907}
    {\#3907 [WIP] Adding tests for estimators implementing
      `partial\_fit` and a few other related fixes / enhancements}}\\
  Commentary: This pull request doesn't quite deal with the tree
  module, and it seems like @rvraghav93 is still actively working on
  it.


  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/3922}
    {\#3922 [WIP] allow nearest neighbors algorithm to be an estimator}}\\
  Commentary: @jnothman seems to have finished most of the work on
  this PR, but it is stalled in the review process. It seems most devs
  are +1 on adding this. I've pinged @jnothman about the current
  status of the pull request, and am waiting for his response.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4191}
    {\#4191 Add Jensen-Shannon distance metric}}\\
  Commentary: This pull request seems to have most of the core
  functionality in place, but it's missing docs and a convincing
  example as to why it should be included. Most of the PR discussion
  centers around whether the Jensen-Shannon distance metric would be
  useful for solving a real applied problem. The original contributor
  seems to have abandoned the project, although I'm not sure there's a
  clear consensus as to whether it would be well received.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4215}
    {\#4215 [MRG] GBM \& meta-ensembles - support for class\_weight}}\\
  Commentary: This pull request seems to have been abandoned, but most
  of the work is completed. Maybe just needs some refactoring before
  another review. Not quite relevant to the tree module, however.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4217}
    {\#4217 [MRG] Neighbors refactor}}\\
  Commentary: This pull request seems mostly completed, and the devs
  were discussing how it would affect performance (the answer seems to
  be minimally, but its not possible to tell completely yet) before it
  went stale. Again, not quite relevant to the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4288}
    {\#4288 [WIP] Allow nan for userdefined metric in dbscan et al}}\\
  Commentary: This pull request seems to have been
  abandoned. Regardless, it does not deal with the tree
  module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4354}
    {\#4354 [WIP] Make GridSearchCV and all estimators support sparse y}}\\
  Commentary: @rvraghav93 is still working on this pull request, and
  is still working on it. There is a temporary standstill because he
  is waiting for sparse y (which he and @betatim) are working on to be
  supported in trees before continuing.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4458}    
    {\#4458 [MRG+1] Implement haversine metric in pairwise}}\\
  Commentary: This pull request seems to have gone stale, but all that
  is needed for its completion is some benchmarking. Again, not quite
  relevant to the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4501}
    {\#4501 [MRG] Add distance threshold on Hierarchical Clustering,
      see \#3796}}\\
  Commentary: This pull request seems to be mostly completed, but
  there are still a few outstanding comments to be addressed. Doesn't
  quite fit in the scope of a project on the tree module.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4522}
    {\#4522 [WIP] Metrics Testing}}\\
  Commentary: This pull request doesn't deal with the tree module, but
  instead works with neighbors / clustering.

  \item 
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4525}
    {\#4525 [MRG+1] Listed valid metrics for neighbors algorithms}}\\
  Commentary: This pull request doesn't work with the tree
  module. However, it seems completed and is just waiting for a
  few more reviews before merge.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4535}
    {\#4535 [WIP] Fortran c order test}}\\
  This PR seems to have gone stale, and is not quite relevant for the
  tree module. Seems like a significant amount of work would be
  required to get this working.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4801}
    {\#4801 Discretization using Fayyad's MDLP stop criterion }}\\
  This PR seems mostly complete, but it seems like most of the devs do
  not know of suitable applications for the code. The original
  developer is still willing to work on the code, in the case that it
  is deemed relevant enough for inclusion.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4844}
    {\#4844 [MRG] Add KNN strategy for imputation}}\\
  This PR seems to have gone stale, however it seems as if its ready
  for review and merging. Regardless, it deals more with NN than the
  tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4848}
    {\#4848 [MRG+1] Multioutput bagging}}\\
  This PR seems complete, and is just waiting for a few more reviews
  before merging.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4899}
    {\#4899 NOCATS: Categorical splits for tree-based learners}}\\
  Currently in active development (mostly by @rvraghav93), and very 
  relevant to the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4926}
    {\#4926 Hdbscan}}\\
  Comments on the PR indicate that it will not be merged into master,
  and is best served as a related project.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4950}
    {\#4950 Add monotonicity parameter to Gradient Boosting and
      Decision Trees}}\\
  This PR seems mostly complete, and doesn't cause many changes in
  time complexity to the tree code. However, it is still debatable
  whether this niche case is worth the added complexity in the tree
  code. Seems like some more discussion is needed, but seems mostly
  complete otherwise.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/4951}
    {\#4951 DOC add official install guide in README.rst}}\\
  Not relevant to the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5099}
    {\#5099 [WIP] Modified LSHForest to check candidates only in
      relevant sections}}\\
  The code seems mostly completed, and is just needing benchmarks that
  demonstrate its benefit over the current implementation of
  LSHForest. @jnothman ran some initial tests, however, and they
  "don't seem to be as positive as I'd hoped." Regardless, it is more
  related to neighbors code than the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5181}
    {\#5181 Balanced Random Forest}}\\
  Seems to have gone stale, but is needing documentation and tests
  before merge. The code seems mostly complete though? This isn't
  quite relevant to the tree module, but it \textbf{could be an
    interesting PR to pick up on the side}.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5279}
    {\#5279 WIP: LOF algorithm (Anomaly Detection)}}\\
  This PR seems to still be in active development.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5333}
    {\#5333 [MRG] pairwise\_distances outputs Nan and negative values}}\\
  This PR seems to have gone slightly stale, but it seems mostly
  complete and is waiting for review.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5382}
    {\#5333 [MRG] pairwise\_distances outputs Nan and negative values}}\\
  This PR seems to be stale, and doesn't seem too relevant to the tree code.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5414}
    {\#5414 [MRG+1] Elkans K means}}\\
  This PR is still in active development, and just needs some reviews
  before it can be merged.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5460}
    {\#5460 [MRG] convert to boolean arrays for boolean distances (ex: jaccard)}}\\
  This PR seems to have gone slightly stale, but generally looks
  complete. Maybe just needs a few more reviews before merging? Not
  too relevant to the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5491}
    {\#5491 [WIP] Gaussian Process-based hyper-parameter optimization}}\\
  This PR is still in active development.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5532}
    {\#5532 Add `return\_std` option to ensembles}}\\
  This PR seems to have slightly stale, but @glouppe might still be
  working on it. Not too relevant to the tree module, moreso for
  ensemble.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5564}
    {\#5564 [WIP] Default dict for GridSearch}}\\
  This PR seems to have gone stale, and isn't too relevant to the tree
  code. \textbf{Not too relevant to a Google Summer of Code proposal on trees, but
    could be something interesting to pick up on the side, though.}

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5593}
    {\#5593 [MRG] ENH: Support threshold='auto' in Birch}}\\
  @mechcoder did say he plans on finishing this PR, but there has been
  no activity since January. Regardless, it is more relevant to the
  cluster module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5596}
    {\#5596 [MRG] Fix NearestNeighbors algorithm='auto' to work with
      all supported metrics by default}}\\
  @mechcoder gave a brief review, but the original author has yet to
  address the comments. \textbf{This PR looks almost complete, but it
    isn't quite relevant to the tree module. Another thing to possibly
    work on on the side}.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5653}
    {\#5653 [WIP] Generalized partial dependence plots}}\\
  This PR is slightly stale as the original author is a bit busy. At
  the moment, its more suited for ensemble / boosted methods than just
  the decision tree. This project also seems fairly big, so it
  is probably out of scope.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5689}
    {\#5689 [MRG] Gradient Boosting Classifier CV}}\\
  This PR seems to have gone slightly stale, but appears to have been
  well received by many contributors. Not relevant to the the tree
  module, however.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5757}
    {\#5757 [MRG+1] fixed IsolationForest(max\_features=0.8).predict(X)
    fails input validation}}\\
  This PR fixes the bug at hand, but causes a memory explosion on
  large datasets, causing it to be 5x slower. Probably needs some more
  discussion / review before it can be merged. Again not quite
  relevant to the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5815}
    {\#5815 \#5789 Expose base estimator iforest}}\\
  PR seems to have gone stale, but seems like there is some
  disagreement about how to move forward with the PR in terms of API /
  confusion with the meaning of various parameters. Not quite relevant
  to the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5825}
    {\#5825 [WIP] Adding Fixed Width Discretization}}\\
  PR seems to have gone slightly stale, and it does not quite apply to
  the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5862}
    {\#5862 Add clarification on random forest regressor default params}}\\
  Docfix that isn't relevant to the tree module. Needs reviewing,
  however.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5963}
    {\#5963 Added subsampling to RandomForest}}\\
  PR seems to have gone stale. Hasn't been quite reviewed yet, so it's
  hard to gauge the level of developer acceptance of the
  feature. Regardless, this PR doesn't apply to the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/5974}
    {\#5974 [MRG] ENH Add support for missing values to Tree based Classifiers}}\\
  @rvraghav93 is actively working on this PR.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6029}
    {\#6029 Adding Time Series Regressors}}\\
  Time Series is generally out of scope in scikit-learn, and this PR
  is unlikely to be merged into master as a result.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6039}
    {\#6039 Add mae regression tree}}\\
  The original maintainer is not working on the PR anymore, but @vene
  and @mechcoder are interested in taking it on. \textbf{This is
    pretty relevant to the tree module, and perhaps would be something
  useful to take on if @vene or @mechcoder are not already working on it.}

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6114}
    {\#6114 Fix docstring signature mismatch in cython code}}\\
  Docfix PR, so not quite relevant to the tree module. This is
  probably a quick fix though, and can be pushed through pretty
  quickly if someone decides to take it up.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6169}
    {\#6169 BestFirstTreeBuilder should ignore tree.max\_depth}}\\
  This is a quick bugfix in the tree module, there should probably be
  some clearer documentation about \texttt{max\_depth} and
  \texttt{max\_leaf\_node} and how \texttt{max\_depth} would not be
  ignored in that case. \textbf{Probably a pretty quick fix if the
    original auathor decides to abandon the PR}. 

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6274}
    {\#6274 [MRG] MAINT: Make sure all tests are included with installation}}\\
  This is a build PR, and is not relevant to the tree module.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6376}
    {\#6376 [MRG+2] Fix for issue \#6352}}\\
  This PR is relevant to the tree module, but it is pretty much
  done. Maybe one more review + merge?

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6380}
    {\#6380 WIP: Add decision tree plotting}}\\
  This PR is relevant to the tree module, but would require fairly
  wide modification in the API to enable functions like
  \texttt{DecisionTreeClassifier/Regressor().plot()} and would thus
  have to go through a full RFC and enhancement proposal. Not really
  any strong opinions about whether it would be worth it to go through
  with submitting a proposal yet.

  \item
  Title:
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6400}
    {\#6400 [MRG] ENH use n\_jobs in brute-force radius\_neighbors}}\\
  This PR is more relevant to the neighbors module than the tree
  module. There haven't been any reviews on it yet.
\end{enumerate}

\section{Summary}
Issues that seem fit for a project would be:
\begin{enumerate}
  \item
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/941}
    {\#941 Adding a pruning method to the tree}}
  \item
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6039}
    {\#6039 Add mae regression tree}}
  \item
  \textbf{\href{https://github.com/scikit-learn/scikit-learn/pull/6169}
    {\#6169 BestFirstTreeBuilder should ignore tree.max\_depth}}
\end{enumerate}
Out of these, \textbf{\#941} and \textbf{\#6039} are the large issues,
and I believe that I could tackle \textbf{\#6169} as well if it's not
complete by the time Google Summer of Code comes around. Additionally, I'm tentatively
planning on taking on a few misc PR's during the summer
(e.g. \textbf{\#5099}) and participating in code reviews / discussions
per usual.
\end{document}
